\sysfull

### 2018-04-15 paper/intro.tex

A savvy programmer may thus create very large tasks in an attempt to minimize
overhead by minimizing the number of task transitions.  However, a very large
task may require more energy to complete than a device's fixed hardware energy
buffer can hold.  Such a large task fails to completely execute assuming only
buffered energy is available (i.e., assuming the worst case).  While some
environments may have sufficient harvestable energy to replenish a device's
capacitor during operation, prolonging the execution period and enabling the
task to complete, assuming cooperation from the physical environment to avoid
non-termination is a risky programming proposition.  To eliminate this risk,
existing systems require the programmer or compiler to decompose a  program
into small tasks, all of which complete using only buffered energy.  These
constraints on task sizing leave an unsatisfying dilemma: large, efficient
tasks that risk non-termination, or small tasks that are guaranteed to
complete, but incur a high task transition and commit overhead.  In this work,
we propose a third way, using a novel technique called {\em adaptive task-execution by dynamic task
coalescing/splitting} that efficiently executes small tasks, avoiding unnecessary overheads while avoiding the risk of non-termination.

>>>>

A savvy programmer may thus create very large tasks in an attempt to minimize
overhead by minimizing the number of task transitions.  However, a very large
task may require more energy to complete than a device's fixed hardware energy
buffer can hold.  Such a large task fails to completely execute assuming only
buffered energy is available (i.e., assuming the worst case).  While some
environments may have sufficient harvestable energy to replenish a device's
capacitor during operation, prolonging the execution period and enabling the
task to complete, assuming cooperation from the physical environment to avoid
non-termination is a risky programming proposition.  To eliminate this risk,
existing systems require the programmer or compiler to decompose a  program
into small tasks, all of which complete using only buffered energy.  These
constraints on task sizing leave an unsatisfying dilemma: large, efficient
tasks that risk non-termination, or small tasks that are guaranteed to
complete, but incur a high task transition and commit overhead.  In this work,
we propose a third way, using a novel technique called {\em adaptive execution by dynamic task
coalescing/splitting} that efficiently executes small tasks, avoiding unnecessary overheads while avoiding the risk of non-termination.

### 2018-04-15 paper/systemdescription.tex

\textbf{\sys Task Coalescing Manager.} \sys relies on its task coalescing manager to dynamically {\em coalesce} statically\hyp{}defined tasks to avoid inessential overheads associated with completing tasks. By default, tasks run in a sequence and each task commits its task-shared state as it completes.  The time and energy cost of a task's commit is unnecessary if the task and its successor both complete without a power failure. The key insight that \sys leverages is that the first task could have deferred its commit to the second task. {\em coalescing} tasks by deferring the first commit avoids the fixed cost of the first commit (task transitioning overheads). Coalescing also amortizes per-variable commit cost, committing each location accessed by both tasks only after the second task, rather than once per task. Details of coalescing are presented in Section~\ref{sec:task_coalescing}.

\textbf{\sys Task Downscaling Manager.} Details of task downscaling are presented in Section~\ref{sec:task_downsizing}. \textcolor{red}{to be written}

>>>>

\textbf{\sys Task Coalescing Manager.} \sys relies on its task coalescing manager to dynamically {\em coalesce} statically\hyp{}defined tasks to avoid inessential overheads associated with completing tasks. By default, tasks run in a sequence and each task commits its task-shared state as it completes.  The time and energy cost of a task's commit is unnecessary if the task and its successor both complete without a power failure. The key insight that \sys leverages is that the first task could have deferred its commit to the second task. {\em coalescing} tasks by deferring the first commit avoids the fixed cost of the first commit (task transitioning overheads). Coalescing also amortizes per-variable commit cost, committing each location accessed by both tasks only after the second task, rather than once per task. \textcolor{red}{\sys's coalescing manager is an \emph{energy-aware manager}. It uses the recent execution history---pure software technique---as a metric to estimate the amount of the available energy and to set the adequate coalesced task size accordingly. This fundamental feature prevents \sys from blind coalesced task adaptation which can result in a repeated power failures problem. For example, If \sys enlarges the coalesced task size by $x$ static tasks on a coalesced task completion and reduces it by the same number of static tasks on a power reboot, then \sys may need to reboot, for instance, 10 times to reduce a coalesced task size from 10 to one, when $x=1$}

Details of coalescing are presented in Section~\ref{sec:task_coalescing}.

\textbf{\sys Task Downscaling Manager.} \sys's downscaling manager is responsible for preserving the forward progress when \sys fails repeatedly on a single static task. The downscaling manager utilizes a timer-based technique to split a big task and ensure a partial progress.

 Details of task downscaling are presented in Section~\ref{sec:task_downsizing}. \textcolor{red}{to be written}

 \textcolor{red}{Why hardware based checkpoint systems are static? and why \sys's partial commit is dynamic?}

\textcolor{red}{(i) Stopping at arbitrary locations in the code may result in incorrect computation or even crash the program. If a system checkpoints between, for example, the DMA initialization and the DMA call the program will crash. One might think that a simple solution is to disable interrupts at these critical regions. Although this is the correct solution, the checkpoint-based system will "theoretically" stuck (non-termination problem) because it has to checkpoint at this exact location since it is a threshold-based system, so it is a static system. However, \sys's partial commit is not threshold based therefore it allows the programmer to disable interrupts at certain locations and it will partially commit around it.}

\textcolor{red}{(ii) A Checkpoint system normally checkpoints all volatile data. Therefore, it suffers from moving large amount of data on each checkpoint. However, \sys's partial commit technique relies on a paging mechanism, which makes the size of the commit proportional to the number of state-less instructions executed. In other words, if energy allows executing only a small chunk of code, the amount of data to be committed shrinks accordingly. As such, \sys's execution model is neither limited by a static task size to progress, nor by the commit size,
}
